Synthesizing by means of mice

### 2020-08-08 mice_synthesizing/Mice_Synthesizing.Rmd
Update with passive imputations for bmi

```{r}
cart_default <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))

cart_adj <- boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))

cart_default

cart_adj
```

>>>>

```{r}
cart_default <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), 
            Between = mean(bm), 
            Total = mean(var),
            .groups = 'drop')

cart_adj <- boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), 
            Between = mean(bm), 
            Total = mean(var),
            .groups = 'drop')

bind_rows("Cart default" = cart_default,
          "Cart adjusted settings" = cart_adj, .id = "Method") %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
